\subsection{Containers}

\begin{itemize}
    \item \textbf{std::vector: } A dynamic array. Most methods give O(1) time complexity for access and O(N) for insertion/deletion (except at the end, which is O(1)).
    \item \textbf{std::list: } A doubly linked list. Most methods give O(1) time complexity for insertion/deletion (given an iterator) and O(N) for access.
    \item \textbf{std::deque: } A double-ended queue. Most methods give O(1) time complexity for access and O(1) for insertion/deletion at both ends, but O(N) for insertion/deletion in the middle.
    \item \textbf{std::stack: } A container adapter that gives the functionality of a stack (LIFO). Most methods give O(1) time complexity for push, pop, and top operations.
    \item \textbf{std::queue: } A container adapter that gives the functionality of a queue (FIFO). Most methods give O(1) time complexity for push, pop, and front/back operations.
    \item \textbf{std::priority\_queue: } A container adapter that gives the functionality of a priority queue. Most methods give O(log N) time complexity for push and pop operations, and O(1) for top operation.
    \item \textbf{std::set: } A sorted associative container that contains unique elements. Most methods give O(log N) time complexity for insertion, deletion, and search operations.
    \item \textbf{std::map: } A sorted associative container that contains key-value pairs with unique keys. Most methods give O(log N) time complexity for insertion, deletion, and search operations.
    \item \textbf{std::unordered\_set: } An unordered associative container that contains unique elements. Most methods give O(1) average time complexity for insertion, deletion, and search operations, but O(N) in the worst case.
    \item \textbf{std::unordered\_map: } An unordered associative container that contains key-value pairs with unique keys. Most methods give O(1) average time complexity for insertion, deletion, and search operations, but O(N) in the worst case.
\end{itemize}
