\subsection{System Solving}

\begin{itemize}
    \item \textbf{Definition: } A \textbf{system of equations} is a set of two or more equations involving the same set of variables. A solution to the system is a set of values for the variables that satisfies all the equations in the system.
    \item \textbf{Methods of Solving: }
          \begin{itemize}
              \item \textbf{Substitution: } Solve one equation for one variable and substitute that expression into the other equation(s).
              \item \textbf{Elimination: } Add or subtract the equations to eliminate one variable, making it easier to solve for the remaining variable(s).
              \item \textbf{Graphical: } Graph the equations on a coordinate plane and identify the point(s) of intersection, which represent the solution(s) to the system.
              \item \textbf{Matrix Method: } Use matrices and row operations to solve systems of linear equations, particularly useful for larger systems.
          \end{itemize}
    \item \textbf{Types of Solutions: }
          \begin{itemize}
              \item \textbf{Unique Solution: } The system has exactly one solution, meaning the equations represent lines (in 2D) or planes (in 3D) that intersect at a single point.
              \item \textbf{Infinite Solutions: } The system has infinitely many solutions, meaning the equations represent the same line (in 2D) or plane (in 3D).
              \item \textbf{No Solution: } The system has no solution, meaning the equations represent parallel lines (in 2D) or planes (in 3D) that do not intersect.
          \end{itemize}
\end{itemize}

\subsection{Linear System Solving}
One of the most common types of systems is a system of linear equations, which can be represented in matrix form as $Ax = b$, where $A$ is the coefficient matrix, $x$ is the variable vector, and $b$ is the constant vector. The solution can be found using LU Decomposition, which factors the matrix $A$ into a lower triangular matrix $L$ and an upper triangular matrix $U$. This allows us to solve the system in two steps: first solving $Ly = b$ for $y$, and then solving $Ux = y$ for $x$.
