\subsection{Built-ins \& Tricks}

\begin{itemize}
    \item \textbf{Big integers: } Python integers have arbitrary precision — no overflow, no \texttt{long long} needed. \texttt{2**1000} works natively.
    \item \textbf{pow(base, exp, mod): } Built-in modular exponentiation in O(log exp). Much faster than \texttt{(base**exp) \% mod}.
    \item \textbf{divmod(a, b): } Returns \texttt{(a // b, a \% b)} in one call.
    \item \textbf{int(s, base): } Converts string \texttt{s} in given base to int. \texttt{int('ff', 16) = 255}, \texttt{int('1010', 2) = 10}.
    \item \textbf{bin / oct / hex: } \texttt{bin(10) = '0b1010'}, \texttt{hex(255) = '0xff'}. Slice \texttt{[2:]} to remove prefix.
    \item \textbf{enumerate: } \texttt{enumerate(lst)} yields \texttt{(index, value)} pairs. Avoids \texttt{range(len(lst))}.
    \item \textbf{zip: } \texttt{zip(a, b)} pairs elements. \texttt{zip(*matrix)} transposes a matrix. \texttt{zip\_longest} from \texttt{itertools} handles unequal lengths.
    \item \textbf{map / filter: } \texttt{list(map(int, input().split()))} reads a line of ints. \texttt{filter(func, lst)} filters in-place lazily.
    \item \textbf{any / all: } \texttt{any(cond(x) for x in lst)} short-circuits on first \texttt{True}. \texttt{all} short-circuits on first \texttt{False}.
    \item \textbf{sorted with key: } \texttt{sorted(lst, key=lambda x: -x)} sorts descending. \texttt{sorted(words, key=len)} sorts by length. Stable sort.
    \item \textbf{min / max with key: } \texttt{max(lst, key=lambda x: x[1])} finds element with max second component.
    \item \textbf{Multiple assignment: } \texttt{a, b = b, a} swaps without a temp variable. \texttt{a, *rest = lst} unpacks head and tail.
    \item \textbf{List comprehension: } \texttt{[f(x) for x in lst if cond(x)]} replaces most filter+map patterns. Faster than equivalent loops.
    \item \textbf{lru\_cache: } \texttt{@functools.lru\_cache(maxsize=None)} memoizes a function. Replaces manual \texttt{dp} dictionaries for recursive solutions.
    \item \textbf{Fast I/O: } Use \texttt{sys.stdin.read().split()} to read all input at once when input is large.
    \item \textbf{Global recursion limit: } Default is 1000. Use \texttt{sys.setrecursionlimit(300000)} for deep recursion.
\end{itemize}

\begin{lstlisting}[language=Python]
import sys, functools
input = sys.stdin.readline  # faster input

# Read line of ints
n, m = map(int, input().split())
arr  = list(map(int, input().split()))

# Modular exponentiation
print(pow(2, 10**9, 10**9 + 7))  # O(log exp)

# Transpose matrix
matrix = [[1,2,3],[4,5,6]]
T = list(map(list, zip(*matrix)))

# Memoized recursion
@functools.lru_cache(maxsize=None)
def dp(i, j):
    if i == 0: return j
    if j == 0: return i
    return min(dp(i-1, j) + 1,
               dp(i, j-1) + 1,
               dp(i-1, j-1) + (s[i-1] != t[j-1]))

# Unpack head/tail
first, *rest = arr

# Flat 2D list comprehension
flat = [x for row in matrix for x in row]

# Read all input at once
data = sys.stdin.read().split()
idx  = 0
n    = int(data[idx]); idx += 1
\end{lstlisting}